MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-05-18 latex/paper/sections/10-placement.tex
sim broken again?

\section{Placement}
    \label{sec:placement}
    Up until now we have only organized the logical \texttt{EDIFHierCellInst}s into \texttt{SiteInst}s. 
    This is where simulated annealing actually begins where we actually place the \texttt{SiteInst}s onto physical \texttt{Site}s on the \texttt{device} level.

>>>>

\section{Placement}
\label{sec:placement}
Up until now, we have only dealt with technology problems where we consider the problem space and adress the constraints of the hardware architecture. 
For every constraint, we devise a solution or a simplification that sacrifices some optimization to reduce the complexity of the problem space.

Now that we have dealt with the bulk of the Cell-BEL level constraints and squared them away into self-contained \texttt{SiteInst}s, we can now apply some well-known optimization algorithms to finally address our optimization objective, which is to place these \texttt{SiteInst}s onto the device in a way that minimizes wirelength.

In this paper we implement and present a Simulating Annealing (SA) placer that operates at the \texttt{SiteInst} level.

\subsection{Simulated Annealing}
\label{subsec:simulated_annealing}

\begin{lstlisting}[language=java, caption={Simulated Annealing pseudocode}, label={lst:sa_pseudocode}]

\end{lstlisting}
